---
title: "NF-OSI milestone report"
date: '`r Sys.Date()`'
output:
  html_document:
    theme: cerulean
    toc_depth: 3
    toc_float: yes

params:
  projectid: NA
  projectname: "No Project"
  fvid: NA
  milestone: 6
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
projectid=params$projectid
projectname=params$projectname
milestone=params$milestone
fv=params$fvid
```

```{r, include = FALSE}
require(synapser)
synLogin()
```
#### `r milestone` milestone report for project `r projectname`
We collected the data promised as part of the [NTAP Milestone Report Survey](https://www.synapse.org/#!Synapse:syn11646002/tables/) with the data in your [Synapse Project](https://www.synapse.org/#Synapse:`r projectid`) for `r milestone`  month milestone and found the following results:

```{r, include = FALSE}
### submitted milestones
### syn11646002
surv_id='syn11646002'
query=paste('SELECT * from',surv_id,'WHERE ( ( "Milestone (months)" =',milestone,'))')
deliverables_survery <-synTableQuery(query)$asDataFrame()
deliverables_survery <- na.omit(deliverables_survery)
```


```{r, include = FALSE}

query <- paste0("select * from ",  fvid, " where projectId = '",projectid,"' and resourceType = 'experimentalData' and reportMilestone = '", milestone, "'")
six_mo_fileview <- synTableQuery(query)$asDataFrame()
```

```{r, include = FALSE}

test_name_deliverables <- subset(deliverables_survery, deliverables_survery$`Project Name` == projectname )


if(nrow(test_name_deliverables)==0){
  test_name_deliverables=data.frame(
      `Project Name`=projectname,
      `Milestone (months)`=milestone,
      `Assay`=ifelse(length(unique(six_mo_fileview$assay)==0),"",paste(unique(six_mo_fileview$assay),sep=',')),
      `Proposed Number of Samples`=0,check.names=F)
}

#get first assay listed (brightfield microscopy )
six_mo_brightfield <- subset(six_mo_fileview, six_mo_fileview$assay == test_name_deliverables$Assay)

if(nrow(six_mo_brightfield)==0){
  #colnames(test_name_deliverables)[6] <- "Proposed number of samples"
  test_name_deliverables$`Actual number of samples` <- 0

}else if ( !is.na(six_mo_brightfield$isMultiSpecimen)) { #for multispecimen samps
  test <- subset(six_mo_brightfield, specimenID != "NA")

  counter = 0
  for (i in seq_along(test$specimenID)) {
    # print(i)
    print(test$specimenID[i])
    specimens <- test$specimenID[i]
    nums <- unlist(strsplit(specimens,","))
    print(length(nums))
    counter = counter + length(nums)
  }
  ### how many specimen IDs there are seperated by commas only though
#  colnames(test_name_deliverables)[6] <- "Proposed number of samples"
  test_name_deliverables$`Actual number of samples` <- counter

} else{
  counter <- length(six_mo_brightfield$dataType)
  colnames(test_name_deliverables)[6] <- "Proposed number of samples"
  test_name_deliverables$`Actual number of samples` <- counter
}

```

#### `r milestone` Month Milestones Table
```{r, echo = FALSE}
library(DT)
datatable(test_name_deliverables[,-c(1,2)],
          class = 'cell-border stripe',
          rownames= FALSE, filter = 'top',
          caption = paste("Table 1: This shows the proposed number of samples by the NTAP Milestone Report Survey and compares it to the number of samples in the",milestone," month deliverables "))
```


```{r, include = FALSE}
library(reshape2)
df <- melt(test_name_deliverables[,-c(1,2)])[-1,]
df$variable <- factor(df$variable, levels = df$variable)
```

#### `r milestone` Month Milestones Graph
```{r, warning=FALSE, echo = FALSE}
library(ggplot2)
```
```{r,echo = FALSE}

ggplot(df, aes(x=variable, y=value)) + geom_bar(stat="identity", aes(fill = variable)) + scale_fill_manual(values= c('#93C3DC','#5A478F')) + ylab("Number of Samples")+ xlab("") + ggtitle(paste(milestone,"Month Milestone report for",projectname)) + guides(fill=FALSE) + theme_minimal()
```

This graph shows the proposed number of samples from the milestone report in blue and the actual number of samples found in the `r milestone` month deliverables folder in purple.
